---
title: "Additional Resources Page"
output:
  html_document:
    number_sections: no
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
library(dplyr)
library(highcharter)
library(knitr)
library(stringr)
library(tidyverse)

knitr::opts_chunk$set(comment=FALSE, message=FALSE, warning=FALSE, echo=FALSE
)

setwd("W:/Project/RDA Team/TNP/R")
```

This page is a hub of existing resources that provide data and stories on six topic areas surrounding child wellness: Demographics, Health, Built Environment, Education, Economic Wellness and Child Safety. Centralizing data makes it easier to draw connections between these different topic areas, all of which exist in relation to each other and require investment and in order for children to truly thrive. Drawing the connections is how we can paint a holistic picture of child wellness.

# Demographics

## Data {.tabset .tabset-pills}

### New Sources

* [City of Long Beach Data Portal](https://datalb.longbeach.gov/)
* [LA Counts](https://www.lacounts.org/)

### Sources used in webpage
```{r}
library(kableExtra)

Topic<-c("Race and Ethnicity", "Children Age 0 to 5", "Racial Generation Gap", "Nativity and Ancestry" )
Source<-c("American Census Survey (ACS)", "American Census Survey (ACS)", "National Equity Atlas", "National Equity Atlas")

Year<-c("2018", "2019", "2017", "2017")


url<-c("https://advancementproject.sharepoint.com/:x:/s/Portal/Ea-6aINlRjdJuWZ_PV9gHw0BbFf4ulpe5liG7S_7U8eqYg?e=gAGe47",
    "https://advancementproject.sharepoint.com/:x:/s/Portal/Ec7LfN3gvjdEuF66wHATGYkBTYWI6L1lntsgGgmCnP3Xbg?e=rp7FcS",
    "https://nationalequityatlas.org/indicators/Racial_generation_gap#/?geo=06000000000006037",
    "https://nationalequityatlas.org/indicators/Nativity-and-ancestry#/?geo=03000000000031100")

table<-data.frame(Topic, Source, Year)

#make table

table %>% 
  mutate(Dataset = cell_spec(("Data link"), "html", link = url)) %>%
  kable("html", escape = FALSE, align="l") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "striped"))%>%
  pack_rows("Zip Code Level", 1, 2, label_row_css = "background-color: #18bc9c; color: #fff;")%>%
  pack_rows("City Level", 3, 4, label_row_css = "background-color: #18bc9c; color: #fff;")



```

## Stories


# Health

## Additional Data Sources


## Data {.tabset .tabset-pills}

### New Sources

* [Covid-19 Race Class Analysis in Los Angeles County](https://www.racecounts.org/covid/)

### Sources used in webapge

## Stories

# Built Environment

## Data {.tabset .tabset-pills}

### New Sources
* [City of Long Beach Flood Zones](https://datalb.longbeach.gov/datasets/3aff2dbcf9bc43ba97a3bf5aa90d82ae_7)
* SmartairLA Page

### Sources used in webapge

## Stories


# Education

## Data {.tabset .tabset-pills}

### New Sources

* [Number of Licesned Day Care Center Slots per 1,000 Children age 0-5](https://www.lacounts.org/dataset/test-cdph-number-of-licensed-daycare-center-slots-per-1-000-children-aged-0-5-years)

### Sources used in webpage

## Stories


# Economic Wellness

## Data {.tabset .tabset-pills}

### New Sources

### Sources used in webpage

## Stories

# Child Safety

## Data {.tabset .tabset-pills}

### New Sources

* [City of Long Beach Crime Incidents](https://longbeachca.maps.arcgis.com/apps/webappviewer/index.html?id=da05d12e09104e598b6ebcace59f2bba)

### Sources used in webpage

## Stories
