---
title: "Additional Resources Page"
output:
  html_document:
    number_sections: no
    css: styles.css
    theme: flatly
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---

<style type="text/css">
  body{
  font-family: Franklin Gothic;
}
</style>

```{r setup, include=FALSE}
library(dplyr)
library(highcharter)
library(knitr)
library(stringr)
library(tidyverse)

knitr::opts_chunk$set(comment=FALSE, message=FALSE, warning=FALSE, echo=FALSE
)

setwd("W:/Project/RDA Team/TNP/R")
```

This page is a hub of existing resources that provide data and stories on six topic areas surrounding child wellness: Demographics, Health, Built Environment, Education, Economic Wellness and Child Safety. Centralizing data makes it easier to draw connections between these different topic areas, all of which exist in relation to each other and require investment and in order for children to truly thrive. Drawing the connections is how we can paint a holistic picture of child wellness.

# Demographics

## Data 

```{r}
library(kableExtra)

Topic<-c("Race and Ethnicity", "Children Age 0 to 5", "Racial Generation Gap", "Nativity and Ancestry" )

Source<-c("American Census Survey (ACS)", "American Census Survey (ACS)", "National Equity Atlas", "National Equity Atlas")


Year<-c("2018", "2019", "2017", "2017")


url<-c("https://advancementproject.sharepoint.com/:x:/s/Portal/Ea-6aINlRjdJuWZ_PV9gHw0BbFf4ulpe5liG7S_7U8eqYg?e=gAGe47",
    "https://advancementproject.sharepoint.com/:x:/s/Portal/Ec7LfN3gvjdEuF66wHATGYkBTYWI6L1lntsgGgmCnP3Xbg?e=rp7FcS",
    "https://nationalequityatlas.org/indicators/Racial_generation_gap#/?geo=06000000000006037",
    "https://nationalequityatlas.org/indicators/Nativity-and-ancestry#/?geo=03000000000031100")

table<-data.frame(Topic, Source, Year)

#make table

table %>% 
  mutate(Dataset = cell_spec(("Data link"), "html", link = url)) %>%
  kable("html", escape = FALSE, align="l") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "striped"))%>%
  pack_rows("Zip Code Level", 1, 2, label_row_css = "background-color: #1BBF91; color: #fff;")%>%
  pack_rows("City Level", 3, 4, label_row_css = "background-color: #1BBF91; color: #fff;")


# 
# * [City of Long Beach Data Portal](https://datalb.longbeach.gov/)
# * [LA Counts](https://www.lacounts.org/)



```

## Stories (Placeholder)


# Health

```{r}
library(kableExtra)

Topic<-c("Race and Ethnicity", "Children Age 0 to 5", "Racial Generation Gap", "Nativity and Ancestry" )

Source<-c("American Census Survey (ACS)", "American Census Survey (ACS)", "National Equity Atlas", "National Equity Atlas")


Year<-c("2018", "2019", "2017", "2017")


url<-c("https://advancementproject.sharepoint.com/:x:/s/Portal/Ea-6aINlRjdJuWZ_PV9gHw0BbFf4ulpe5liG7S_7U8eqYg?e=gAGe47",
    "https://advancementproject.sharepoint.com/:x:/s/Portal/Ec7LfN3gvjdEuF66wHATGYkBTYWI6L1lntsgGgmCnP3Xbg?e=rp7FcS",
    "https://nationalequityatlas.org/indicators/Racial_generation_gap#/?geo=06000000000006037",
    "https://nationalequityatlas.org/indicators/Nativity-and-ancestry#/?geo=03000000000031100")

table<-data.frame(Topic, Source, Year)

#make table

table %>% 
  mutate(Dataset = cell_spec(("Data link"), "html", link = url)) %>%
  kable("html", escape = FALSE, align="l") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "striped"))%>%
  pack_rows("Zip Code Level", 1, 2, label_row_css = "background-color: #1BBF91; color: #fff;")%>%
  pack_rows("City Level", 3, 4, label_row_css = "background-color: #1BBF91; color: #fff;")



# * [Covid-19 Race Class Analysis in Los Angeles County](https://www.racecounts.org/covid/)

```


## Stories (Placeholder)

# Built Environment

```{r}
library(kableExtra)

Topic<-c("Race and Ethnicity", "Children Age 0 to 5", "Racial Generation Gap", "Nativity and Ancestry" )

Source<-c("American Census Survey (ACS)", "American Census Survey (ACS)", "National Equity Atlas", "National Equity Atlas")


Year<-c("2018", "2019", "2017", "2017")


url<-c("https://advancementproject.sharepoint.com/:x:/s/Portal/Ea-6aINlRjdJuWZ_PV9gHw0BbFf4ulpe5liG7S_7U8eqYg?e=gAGe47",
    "https://advancementproject.sharepoint.com/:x:/s/Portal/Ec7LfN3gvjdEuF66wHATGYkBTYWI6L1lntsgGgmCnP3Xbg?e=rp7FcS",
    "https://nationalequityatlas.org/indicators/Racial_generation_gap#/?geo=06000000000006037",
    "https://nationalequityatlas.org/indicators/Nativity-and-ancestry#/?geo=03000000000031100")

table<-data.frame(Topic, Source, Year)

#make table

table %>% 
  mutate(Dataset = cell_spec(("Data link"), "html", link = url)) %>%
  kable("html", escape = FALSE, align="l") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "striped"))%>%
  pack_rows("Zip Code Level", 1, 2, label_row_css = "background-color: #1BBF91; color: #fff;")%>%
  pack_rows("City Level", 3, 4, label_row_css = "background-color: #1BBF91; color: #fff;")



# * [City of Long Beach Flood Zones](https://datalb.longbeach.gov/datasets/3aff2dbcf9bc43ba97a3bf5aa90d82ae_7)
#* SmartairLA Page

```


## Stories (Placeholder)

# Education

```{r}
library(kableExtra)

Topic<-c("Race and Ethnicity", "Children Age 0 to 5", "Racial Generation Gap", "Nativity and Ancestry" )

Source<-c("American Census Survey (ACS)", "American Census Survey (ACS)", "National Equity Atlas", "National Equity Atlas")


Year<-c("2018", "2019", "2017", "2017")


url<-c("https://advancementproject.sharepoint.com/:x:/s/Portal/Ea-6aINlRjdJuWZ_PV9gHw0BbFf4ulpe5liG7S_7U8eqYg?e=gAGe47",
    "https://advancementproject.sharepoint.com/:x:/s/Portal/Ec7LfN3gvjdEuF66wHATGYkBTYWI6L1lntsgGgmCnP3Xbg?e=rp7FcS",
    "https://nationalequityatlas.org/indicators/Racial_generation_gap#/?geo=06000000000006037",
    "https://nationalequityatlas.org/indicators/Nativity-and-ancestry#/?geo=03000000000031100")

table<-data.frame(Topic, Source, Year)

#make table

table %>% 
  mutate(Dataset = cell_spec(("Data link"), "html", link = url)) %>%
  kable("html", escape = FALSE, align="l") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "striped"))%>%
  pack_rows("Zip Code Level", 1, 2, label_row_css = "background-color: #1BBF91; color: #fff;")%>%
  pack_rows("City Level", 3, 4, label_row_css = "background-color: #1BBF91; color: #fff;")




# * [California Early Child Care Facilities Report (APCA)](https://www.advancementprojectca.org/ece-facilities)
# * [Number of Licesned Day Care Center Slots per 1,000 Children age 0-5](https://www.lacounts.org/dataset/test-cdph-number-of-licensed-daycare-center-slots-per-1-000-children-aged-0-5-years)


```


## Stories (Placeholder)


# Economic Wellness

```{r}
library(kableExtra)

Topic<-c("Race and Ethnicity", "Children Age 0 to 5", "Racial Generation Gap", "Nativity and Ancestry" )

Source<-c("American Census Survey (ACS)", "American Census Survey (ACS)", "National Equity Atlas", "National Equity Atlas")


Year<-c("2018", "2019", "2017", "2017")


url<-c("https://advancementproject.sharepoint.com/:x:/s/Portal/Ea-6aINlRjdJuWZ_PV9gHw0BbFf4ulpe5liG7S_7U8eqYg?e=gAGe47",
    "https://advancementproject.sharepoint.com/:x:/s/Portal/Ec7LfN3gvjdEuF66wHATGYkBTYWI6L1lntsgGgmCnP3Xbg?e=rp7FcS",
    "https://nationalequityatlas.org/indicators/Racial_generation_gap#/?geo=06000000000006037",
    "https://nationalequityatlas.org/indicators/Nativity-and-ancestry#/?geo=03000000000031100")

table<-data.frame(Topic, Source, Year)

#make table

table %>% 
  mutate(Dataset = cell_spec(("Data link"), "html", link = url)) %>%
  kable("html", escape = FALSE, align="l") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "striped"))%>%
  pack_rows("Zip Code Level", 1, 2, label_row_css = "background-color: #1BBF91; color: #fff;")%>%
  pack_rows("City Level", 3, 4, label_row_css = "background-color: #1BBF91; color: #fff;")




#* [Long Beach Homeless Count](http://www.longbeach.gov/health/services/directory/homeless-services/homeless-count/)



```


## Stories (Placeholder)

# Child Safety

```{r}
library(kableExtra)

Topic<-c("Race and Ethnicity", "Children Age 0 to 5", "Racial Generation Gap", "Nativity and Ancestry" )

Source<-c("American Census Survey (ACS)", "American Census Survey (ACS)", "National Equity Atlas", "National Equity Atlas")


Year<-c("2018", "2019", "2017", "2017")


url<-c("https://advancementproject.sharepoint.com/:x:/s/Portal/Ea-6aINlRjdJuWZ_PV9gHw0BbFf4ulpe5liG7S_7U8eqYg?e=gAGe47",
    "https://advancementproject.sharepoint.com/:x:/s/Portal/Ec7LfN3gvjdEuF66wHATGYkBTYWI6L1lntsgGgmCnP3Xbg?e=rp7FcS",
    "https://nationalequityatlas.org/indicators/Racial_generation_gap#/?geo=06000000000006037",
    "https://nationalequityatlas.org/indicators/Nativity-and-ancestry#/?geo=03000000000031100")

table<-data.frame(Topic, Source, Year)

#make table

table %>% 
  mutate(Dataset = cell_spec(("Data link"), "html", link = url)) %>%
  kable("html", escape = FALSE, align="l") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "striped"))%>%
  pack_rows("Zip Code Level", 1, 2, label_row_css = "background-color: #1BBF91; color: #fff;")%>%
  pack_rows("City Level", 3, 4, label_row_css = "background-color: #1BBF91; color: #fff;")




#* [City of Long Beach Crime Incidents](https://longbeachca.maps.arcgis.com/apps/webappviewer/index.html?id=da05d12e09104e598b6ebcace59f2bba)


```


## Stories (Placeholder)
