---
title: Data Resources Page 
output:
  html_document:
    number_sections: no
    theme: paper
    css: styles.css
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
### Set up workspace ####
#install.packages("extrafont")
library(extrafont)
library(here)
library(dplyr)
library(data.table)
library(tidycensus)
library(sf)
library(ggplot2)
library(RPostgreSQL)
library(formattable)
library(svglite)
library(stringr)
library(tidyr)
library(showtext)
library(scales)
library(kableExtra)
#install.packages("flextable")
library(flextable)
library(DT)
options(scipen=999)

# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL")

con <- dbConnect(drv, dbname = "tnp",
                   host = "aws-postgres-db.c5udgz7ro8hq.us-west-2.rds.amazonaws.com", port = 5432,
                   user = "postgres", password = "password")

knitr::opts_chunk$set(comment=FALSE, message=FALSE, warning=FALSE, echo=FALSE
)

setwd("W:/Project/RDA Team/TNP/R")
```

```{r, include=FALSE}
## FONTS ##
# Step 1: Download fonts (Gotham Bold and Gotham Book) 
# Step 2: Load the downloaded fonts into the R script:
# General: See tutorial here, under "THE SHOWTEXT PACKAGE" section: https://r-coder.com/custom-fonts-r/#The_showtext_package 
# Step 3: Run the code below in each R script

font_add(family = "GothamBold", regular = "C:/Windows/Fonts/Gotham-Bold 700.otf")
font_add(family = "GothamBook", regular = "C:/Windows/Fonts/Gotham-Book 325.otf")

showtext_auto()

# define fonts in chart
font_title <- "GothamBold"
font_subtitle <- "GothamBook"
font_caption <- "GothamBook"
font_bar_label <- "GothamBold"
font_axis_label <- "GothamBook"
font_table_text<-"GothamBook"
```

This page is a hub of data resources that speak to the condition of children in the Central Long Beach and/or Wilmington area. Detailed methodological information for all the data points presented in the report and website can be found under the 'Data Methodology' and 'Crosswalk' sections of this page, and additional data that are not in the report or website but relevant to the conditions of children can be found in the 'Data Library' section. Data can be an empowering tool when it is democratized and put directly in the hands of change-agents. By providing this page, we hope that the information presented in the report will be better understood and more importantly, that partnering organizations and community members can easily explore the data themselves and tailor it to their own needs. 


# Data in the Report

This table contains the data source and methodology information for all of the data indicators that are present in the report and website. Clicking on the link o will navigate you to where in the website or report the indicator is. 

```{r}
#one giant DT for all visuals

library(readxl)

table<-read_xlsx("W:/Project/RDA Team/TNP/R/Data Methodology DT.xlsx", sheet="final")

table%>%
  select(-2)%>%
datatable(
          rownames = FALSE,
          
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    pageLength=4, autoWidth=TRUE,
      columnDefs = list(list(className = 'dt-center', targets = "_all")),
    buttons = c('copy', 'print', 'excel')))


```


# Additional Data Resources

```{r}
table2<-read_xlsx("W:/Project/RDA Team/TNP/R/Data Methodology DT.xlsx", sheet="additional")

datatable(table2, 
          rownames = FALSE, escape=FALSE,
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    autoWidth=TRUE,
      columnDefs = list(list(className = 'dt-center', targets = "_all")),
    buttons = c('copy', 'print', 'excel')))




```


```{r, include=FALSE}

###OLD VERSION###


Topic<-c("Race and Ethnicity", "Children Age 0 to 5", "Language Spoken", "Nativity Status by Race", "Family Composition" )


Description<-c("Race and ethnicity of children Age 0 to 5", 
               "Number and percentage of children Age 0 to 5",
               "Language spoken among children Age 0 to 5",
               "Family head of households born inside and outside of the US by race",
               "Families with married, single male or single female head of households")

Geography<-c("Region 4","Region 4","Region 4","Region 4","Region 4")

Source<-c("American Census Survey (ACS)", "American Census Survey (ACS)", "American Census Survey (ACS)", "PUMS", "American Census Survey (ACS)")


Year<-c("2019","2019","2019","2019","2019")


url<-c("https://advancementproject.sharepoint.com/:x:/s/Portal/Ea-6aINlRjdJuWZ_PV9gHw0BbFf4ulpe5liG7S_7U8eqYg?e=gAGe47",
    "https://advancementproject.sharepoint.com/:x:/s/Portal/Ec7LfN3gvjdEuF66wHATGYkBTYWI6L1lntsgGgmCnP3Xbg?e=rp7FcS",
    "https://nationalequityatlas.org/indicators/Racial_generation_gap#/?geo=06000000000006037",
    "https://nationalequityatlas.org/indicators/Nativity-and-ancestry#/?geo=03000000000031100",
       "https://nationalequityatlas.org/indicators/Nativity-and-ancestry#/?geo=03000000000031100" )

table<-data.frame(Topic, Description,Geography, Source, Year)

#make table

table %>% 
  mutate(Dataset = cell_spec(("Data link"), "html", link = url)) %>%
  kable("html", escape = FALSE, align="l") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "striped"), full_width=F)%>%
  pack_rows("Zip Code Level", 1, 2, label_row_css = "background-color: #1BBF91; color: #fff;")%>%
  pack_rows("City Level", 3, 4, label_row_css = "background-color: #1BBF91; color: #fff;")


```



# Geography Crosswalks 

Calculations for visualizations in this project were created by Advancement Project California. Visualizations are presented at various geographic levels for the Central Long Beach and Wilmington Best Start Geographies. Below you will find the crosswalk for the geography calculations Advancement Project made to analyze data at the Central Long Beach and Wilmington Best Start Geography level. 


```{r}
###zip crosswalk TABLE

zip<-dbGetQuery(con, "SELECT * FROM reg4_zip_crosswalk")%>%
  select(1,4)

# zip%>%
#   kbl(col.names=c("Best Start", "Zip Code"))%>%
#     kable_styling(bootstrap_options = c("striped", "hover","condensed","responsive", full_width = T))

datatable(zip, colnames = c("Best Start", "Zip Code"),
          rownames = FALSE,
          # options = list(
          #   columnDefs = list(list(className = 'dt-center', targets = "_all")),
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    autoWidth=TRUE,
      columnDefs = list(list(className = 'dt-center', targets = "_all")),
    buttons = c('copy', 'print', 'excel')))


```

## PUMA Crosswalk

```{r}

#SAVE for cute puma best start map?


```

```{r}
puma<-dbGetQuery(con, "SELECT * FROM reg4_puma_crosswalk")%>%
  select(1,3,4)

# puma%>%
#   kbl(col.names=c("Best Start", "GEOID", "PUMA"))%>%
#     kable_styling(bootstrap_options = c("striped", "hover","condensed","responsive", full_width = F))


datatable(puma, colnames = c("Best Start", "GEOID", "PUMA"),
          rownames = FALSE,
           # options = list(
           #  columnDefs = list(list(className = 'dt-center', targets = "_all")),
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    autoWidth=TRUE,
      columnDefs = list(list(className = 'dt-center', targets = "_all")),
    buttons = c('copy', 'print', 'excel')))

```

## Census Tract Crosswalk


```{r}
ct<-dbGetQuery(con, "SELECT * FROM reg4_ct_crosswalk")%>%
  mutate(name_full=paste0('Census Tract ',name))%>%
  select(1,7,12)

# ct%>%
#   kbl(col.names=c("Best Start", "GEOID", "Census Tract"))%>%
#     kable_styling(bootstrap_options = c("striped", "hover","condensed","responsive", full_width = F))

datatable(ct, colnames = c("Best Start", "GEOID", "Census Tract"),
          rownames = FALSE,
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    autoWidth=TRUE,
      columnDefs = list(list(className = 'dt-center', targets = "_all")),
    buttons = c('copy', 'print', 'excel')))

  

```



